\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
\bibliographystyle{ieeetr} 
\begin{thebibliography}{22}



\bibitem{} "User:Amritpal\_singh/gsoc\_proposal - BRL-CAD", Brlcad.org, 2017. [Online]. Available: https://brlcad.org/wiki/User:Amritpal\_singh/gsoc\_proposal. [Accessed: 27- Nov- 2017].

\bibitem{} "Dev logs of Rebar Addon for FreeCAD - GSoC project", FreeCAD Forum, Amritpal Singh, 2017. [Online]. Available: https://forum.freecadweb.org/viewtopic.php?f=8\&t=22760. [Accessed: 27- Nov- 2017].

\bibitem{} "FreeCAD User Manual/Documentation", 2017. [Online]. Available: https://www.freecadweb.org/wiki/Main\_Page. [Accessed: 27- Nov- 2017].

\bibitem{} "FreeCAD Tutorial: New Rebar Tools" Youtube, 2017 [Online]. Available: https://youtu.be/BYQQjEKmx5E. [Accessed: 17- Nov- 2017]

\bibitem{} "FreeCAD/FreeCAD", GitHub, 2011. [Online]. Available: https://github.com/FreeCAD/FreeCAD. [Accessed: 27- Nov- 2017].

\bibitem{} "User:Amritpal\_singh/GSoC17/logs - BRL-CAD", Brlcad.org, 2017. [Online]. Available: https://brlcad.org/wiki/User:Amritpal\_singh/GSoC17/logs/. [Accessed: 27- Nov- 2017].

\bibitem{} "amrit3701/FreeCAD-Reinforcement", GitHub, 2017. [Online]. Available: https://github.com/amrit3701/FreeCAD-Reinforcement. [Accessed: 27- Nov- 2017].
\bibitem{} "Doxygen: Main Page", Doxygen.org, 2017. [Online]. Available: http://www.doxygen.org. [Accessed: 27- Nov- 2016].

\bibitem{} "FreeCAD", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/FreeCAD. [Accessed: 27- Nov- 2017].

\bibitem{} http://www.freecadweb.org/

\bibitem{} "MakerBot Customizer", Customizer.makerbot.com, 2016. [Online]. Available: http://customizer.makerbot.com/docs. [Accessed: 27- Nov- 2016].

\bibitem{} "User Interface for Customizing Models", amarjeetkapoor1, 2016. [Online]. Available: https://amarjeetkapoor1.wordpress.com/2016/07/04/user-interface-for-customizing-models/. [Accessed: 27- Nov- 2016].

\bibitem{} "PySide", Wiki - qt, 2017. [Online]. Available: https://wiki.qt.io/PySide\_Tutorials. [Accessed: 27- Nov- 2017].

\bibitem{} "Qt (software)", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Qt\_(software)\#/media/File:Qt\_logo\_2015.svg. [Accessed: 27- Nov- 2017].

\bibitem{} "Git", En.wikipedia.org, 2017. [Online]. Available: 
https://en.wikipedia.org/wiki/Git. [Accessed: 27- Nov- 2017].

\bibitem{}"Qt (software)", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Qt\_(software). [Accessed: 27- Nov- 2017].

\bibitem{} "Python", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Python. [Accessed: 27- Nov- 2017].

\bibitem{}"Travis CI", En.wikipedia.org, 2017. [Online]. Available: https://en.wikipedia.org/wiki/Travis\_CI. [Accessed: 27- Nov- 2017].

\end{thebibliography}
