\section{Dependencies}
Dependencies include softwares or framework that need to be installed for proper working of this software.

This addon could be installed on any given list of operating system.

\begin{enumerate}
	\item Mac OS X
	\item Windows
	 \begin{enumerate} 
	 	\item XP or newer on x86 32/64 bit
	 \end{enumerate}
	\item Linux
	\begin{enumerate} 
		\item Debian 
		\item Ubuntu 
		\item Kubuntu
		\item Arch Linux
		\item openSUSE
		\item Fedora
	 \end{enumerate}
	\item BSD
	\begin{enumerate}
		\item NetBSD  $\geq 6.1$
		\item FreeBSD $\geq 10 $
		\item OpenBSD
	\end{enumerate}
\end{enumerate}	 
 

But If you want to run thepoet.me on your system from soucre code on \emph{any OS}, you need some libraries and tools. The version
numbers in brackets specify the versions which have been used for
development. Other versions may or may not work as well.

If you're using a newer version of Ubuntu, you can install these 
libraries from aptitude. If you're using Mac, or an older Linux/BSD, there 
are build scripts that download and compile the libraries from source. 
Follow the instructions for the platform you're compiling on below. Following are
dependencies of thepoet.me.

\begin{enumerate} 

\item python-decouple
\item django
\item django\_countries
\item django-avatar
\item easy\_thumbnails
\item sorl-thumbnail
\item social-auth-app-django
\item mysqlclient
\item django-image-cropping
\item python-social-auth
\item pyjwkest
\item libmysqlclient-dev
\item libapache2-mod-wsgi-py3

\end{enumerate}
