\section{Product Perspective}

This site is supposed to be part of an open source, under the GNU general Public License. It offers registered user a simple platform from which to link his/her published book and popular social networking websites such as Facebook, Twitter and Instagram. It is characterized by its one-page user profiles, each with a large, often-artistic background and abbreviated biography.

The following are the main features that are included in thepoet.me

\begin{enumerate}
    \item \textbf{Web Compatibility:} The site easily render on various resolutions, screen sizes, and browsers; and with the increasing popularity of mobile devices, it function properly on the plethora of these types of devices.
    \item \textbf{Search Engine Optimisation:} The site generally receive many visitors, and one method to attract visitors is search engine optimisation. The site is optimised with Google search Engine.
    \item \textbf{Simple and Professional Web Design:} There are countless platforms out there that you can use to build your own free personal website, but not all of them will deliver the same sense of quality and professionalism. If you’re a poet or writer and looking for something fast and simple that you just need to represent a landing page for yourself, thepoet.me could be one of your best alternatives to choose from.
    \item \textbf{Clear, User-friendly Navigation:} The site contain a user-friendly navigation scheme that allows visitors to quickly find the information needed. Important links must be easy to find and given logical, simple, and include easy-to-understand labels. Calls to action are placed in conspicuous spots within the navigation’s scheme.
\end{enumerate}  
