\section{Conclusion}

This project was something which required in-depth view in structural engineers field and analysis of your problems. Worked on a Google Summer of Code (GSoC) project with FreeCAD. This project is purely related structural engineering, aimed at easing up the reinforcement process in the FreeCAD. For better user experience, list of basic shapes of rebars are implemented under Rebar tools in the form of dropdown. While normal users can use them in real world complex structures, the same codebase can be used as a platform for implementing advanced rebar shapes.

A great deal of things are learned while working on this project. The learning was not limited to project only but
the whole experience of working as a trainee under Dr. H.S. Rai at TCC, developer at FreeCAD and also as a mentor for Google Code In was immensely educational. Working with the Open Source Community and a variety of people of different age group, one is always challenged by the fundamental difference between classroom coaching and real World experience. But such a challenge is exactly the purpose of six months training.

The whole experience of working on this project and contributing to a few others has been very
rewarding as it has given great opportunities to learn new things and get a firmer grasp on already
known technologies. Here is a reiteration of some of the technologies I have encountered, browsed and learned:
\begin{enumerate}
    \item Operating System: Linux
    \item Language: Python, PySide, IfcOpenShell, C++, \LaTeX
    \item FrameWork: Qt, Django, Django Rest framework
    \item API: Faebook Graph API, Social Auth
    \item Softwares: Git, QtCreator, Inkscape, Doxygen
    \item Building Tools: CMake, make
    \item Communication tools: IRC, Gitter
\end{enumerate}
So during this project, I learned all the above things. Above all, I got to know how software is
developed and how much work and attention to details is required in building even the most basic
of components of any project. Apart from above I also learned things like:
\begin{enumerate}
    \item Planning
    \item Designing
    \item Developing code
    \item Working in a team
    \item Testing
    \item Licensing Constraints
    \item How Open source community work?
    \item Writing Readable code
    \item Coding Standards
\end{enumerate}
And these are all very precious lessons in themselves.
